Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-06-19 BPM17-demo-paper/paper.tex
wording

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been trained, they can be transferred to the Runtime component to make predictions for ongoing cases. As an input, Nirdizati Runtime takes a stream of events produced by a workflow management system (WFMS) that registers tasks performed in the organization. (Figure~\ref{fig:dfd_0}). Next, the produced stream is consumed by a web server which is responsible for storing data and further information processing.
Web server, in turn, communicates with a predictive engine which applies models obtained via Nirdizati Training for a business process and returns all the results of calculations.
After web server receives the outputs from each predictive model, it writes them to a database and updates corresponding clients.
From the user's side, the results are visualized via a dashboard-based interface which is capable of sending queries requesting various visualization options.

>>>>

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been trained, they are used by the Runtime component to make predictions for ongoing cases. As an input, Nirdizati Runtime takes a stream of events produced by information system that register tasks performed in the organization (Figure~\ref{fig:dfd_0}). Next, the produced stream is consumed by a web server which is responsible for storing data and further information processing.
Web server, in turn, communicates with a predictive engine which applies models obtained via Nirdizati Training for a business process and returns all the results of calculations.
After web server receives the outputs from each predictive model, it writes them to a database and updates corresponding clients.
From the user's side, the results are visualized via a dashboard-based interface which is capable of sending queries requesting various visualization options.
